\begin{enumerate}
\bibitem{state_of_art} Facial Expression Recognition using Convolutional Neural Networks: State of the Art
\bibitem{method_1}Y. Tang, “Deep Learning using Support Vector Machines,” in International Conference on Machine Learning (ICML) Workshops, 2013
\bibitem{method_2}B.-K. Kim, J. Roh, S.-Y. Dong, and S.-Y. Lee, “Hierarchical committee
of deep convolutional neural networks for robust facial expression
recognition,” Journal on Multimodal User Interfaces, pp. 1–17, 2016
\bibitem{method_3}Z. Yu and C. Zhang, “Image based static facial expression recognition
with multiple deep network learning,” in ACM International Conference
on Multimodal Interaction (MMI), 2015, pp. 435–442
\bibitem{method_4} A. Mollahosseini, D. Chan, and M. H. Mahoor, “Going Deeper in Facial
Expression Recognition using Deep Neural Networks,” CoRR, vol. 1511,
2015.
\bibitem{method_5}Z. Zhang, P. Luo, C.-C. Loy, and X. Tang, “Learning Social Relation
Traits from Face Images,” in Proc. IEEE Int. Conference on Computer
Vision (ICCV), 2015, pp. 3631–3639
\bibitem{method_6} B.-K. Kim, S.-Y. Dong, J. Roh, G. Kim, and S.-Y. Lee, “Fusing Aligned
and Non-Aligned Face Information for Automatic Affect Recognition in
the Wild: A Deep Learning Approach,” in IEEE Conf. Computer Vision
and Pattern Recognition (CVPR) Workshops, 2016, pp. 48–57.
\bibitem{hog} Carlos Orrite, Andres Ganan, and Gregory Rogez, “HOG-Based Decision Tree for Facial ExpressionClassification”,2009.
%Carlos Orrite, Andr´es Ga˜n´an, and Gr´egory Rogez, “HOG-Based Decision Tree for Facial ExpressionClassification”,2009.
\bibitem{haar} Paul Viola and Michael, "Rapid Object Detection using a Boosted Cascade of Simple Features" in 2001
\bibitem{PCN} Real-Time Rotation-Invariant Face Detection with Progressive Calibration Networks
\end{enumerate}
